\documentclass{article}

% Language setting
% Replace `english' with e.g. `spanish' to change the document language
\usepackage[english]{babel}

% Set page size and margins
% Replace `letterpaper' with `a4paper' for UK/EU standard size
\usepackage[letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

\title{Problem Set 1}
\author{Murphy Chesley}

\begin{document}
\maketitle

 \section{Brief Summary}
 
    I am interested in economics because I think it is the thread that ties us all together. I find educational and environmental economics to be the most interesting as they are both relevant issues for current policies. I think it is really important that when we try to make large-scale changes to societal attitudes or policies, we have empirical evidence supporting the change. It would be great if I could contribute to that evidence and create a better understanding for the public.
    
    I took this class because I felt it would be a good way to learn programming as it relates to economics. The BA/MA has a big data section as well, so this class would fit well within that. I am pretty unfamiliar with coding so I will probably be frequenting office hours a lot! I also think that learning how data science falls into economics is great as learning the coding is good, but having real applications is better.
    
    I will likely want to do my project on behavior patterns in schools and educational outcomes of those issues. Both my two sisters and dad are school teachers here in Norman at Irving Middle School and Kennedy Elementary. Those schools are pretty low income and most kids suffer from learning disabilities and behavioral issues. I see the effect that poor behavior has on teachers and want to see what the result is on the students they teach. 
    
    My goal for this class is to be able to use R with greater fluency and independence. Like I mentioned, a lot of coding material fly right over my head, so I want to really get a better foundation of how to use different programs. After graduation, I am looking into economic research or banking. I am not too sure where I will end up yet, but I hope to leave Oklahoma for a few years and see some place new!

\section{Equation}

$$a^2 + b^2 = c^2$$

 
\end{document}